Staged Abstract Interpreters

### 2019-03-21 paper/10_intro.tex
misc

\paragraph{Abstraction, Abstraction, and Abstraction}
To enable such flexibility between different semantics, we extensively use
abstract type members over multiple abstractions, which can be later instantiated.

>>>>

\paragraph{Abstraction, Abstraction, and Abstraction}
To enable such flexibility between different semantics, we extensively use generic 
programming and abstract type members over multiple abstractions, which can be 
later instantiated.
